\documentclass[12pt,letterpaper]{article}
    \usepackage[utf8]{inputenc}
    \usepackage{ifpdf}
    \usepackage{mla}
    \usepackage[pass]{geometry}
    \usepackage{todonotes}
    \usepackage[hidelinks]{hyperref}

    \urlstyle{same}

\begin{document}
\begin{mla}{Bernardo}{Meurer}{Professor Eckford-Prossor}{English 111 H}{February 28, 2018}{Essay 2 --- 321's}
    \subsection*{3 --- Quotations}
    \begin{itemize}
        \item ``Imprimis, In the right Coat-Pocket of the  Great Man Mountain \ldots Signed and Sealed on the fourth Day of the eighty ninth Moon of your Majesty's auspicious Reign'' (28--30)
              \newline
              --- This passage, which is the inventory report given by the Liliputian inspectors of the belongings of Gulliver, is one of the most explicit uses of the subverted Other as a tool for expliciting the other in the book. What we see here is the use of a meticulous description of things which are familiar to us, but done in such a way where it isn't clear what exactly they are. The Mini Essay contains another example of this form of description, which is an extremely effective way to expose otherness. Here, when we say Other, we refer to the Lacanian Big Other, or in Žižekian terms Ideology, Otherness is then partially related to the Wittgensteinian notion of means as a message. The little other, is yet another Lacanian concept that can be simplified as being just other people, so to speak of one's own otherness is to speak of one perceiving oneself through the eyes of the other, and breaking with the sense of normality that generally veils the analysis of that which is common or known. The idea we want to explore is that Satire subverts the Other (language) to allow the self to be seen thought the eyes of the other, and thus weakening the Borromean knot of reality by causing the Symbolic to disconnect with the Real.

        \item ``And I was privately assured, the Empress conceiving the greatest Abhorrence of what I had done, removed to the most distant side of the Court, firmly resolved that those Buildings should never be repaired for her Use; and, in the presence of her chief Confidents, could not forbear vowing Revenge.''
              \newline
              --- This is a good example of how Satire can be used to employ hidden criticism that allows the writer to subvert the Other (symbolic other) in order to force the reader (being criticized) to see the character being written about as a (little) other, while in fact the character is the reader himself. In other words, this is an example of Satire acting as an ideological bypass, allowing one to see their own otherness.

        \item ``That in some Fields of his Country, there are certain shining Stones of several Colors, whereof the Yahoos are violently fond \ldots''
              \newline
              --- Here we see another nice example of the subversion of the Other. Clearly Swift is referring to the British materialism, and yet while reading one might not realize this at first. It is perfectly reasonable to imagine a wealthy British man reading this passage and thinking to himself that the Yahoos are savages, before realizing he is himself a Yahoo, by which point it is too late as he has already seen himself through the eyes of the other
    \end{itemize}
    \subsection*{2 --- Questions}
    \begin{itemize}
        \item Is the kernel of Satire that it allows us to see our own ``otherness'' in a lacanian sense? --- This question sprouted from reading \textit{Body Ritual Among the Nacirema}, and realizing a link between it, and Gulliver's Travels. The question is equivalent to asking whether that link is this bypass of the Other to allow one to see oneself as the other.
        \item Is the ``poison pill'' aspect of satire, that it allows the one being criticized to read the critique before even acknowledging it as such, possible today? --- From watching modern ``satire'', this follows naturally, given that the previous point being proven (as shall be done in either the mini essay, or the final essay,) the lack of said factor (the bypassing factor) would make the ``satire'' in question (late night shows \textit{et al.}) not truly satire at all.
    \end{itemize}
    \subsection*{1 --- Essay}
    \paragraph*{Satire, Otherness, and Ideology}  \hspace{0pt} \\
    We see the world through Ideological Lens, that cause us to observe the world around us as being ``normal,'' in fact, Ideology itself is what causes us to define as normal that which we see daily and commonly. This idea, presented throughout Slavoj Žižek's work, is tightly knit with the Lacanian concept of the (big) Other, for Ideology becomes itself the symbolic order, which follows from a quasi-Wittgensteinian approach to to influence of the symbolic in the self. In distinction, the (little) other (notice the differentiation in the terms given by capitalization) refers solely to others as in other people, exteriorness. The Satirical has as its unifying feature the effort to subvert the Other (language), bypassing Ideology, in order to allow one to see oneself through the eyes of the other.

    As an experiment, in order to show the subversion of the Other, imagine the first Man who, in his explorations, came across a strange, short, tree with uncommonly large, glossy leafs. On it grew, from some top branches that held a flower-like structure in its end, large groups of bow-shaped, cylinder-like, green and yellow semi-branches. The natives of this land seem to take only the semi-branches of a particular color, and open it to find a soft, white kernel which they eat. Although the description above might seem like that of an extraterrestrial encounter with a nature far differing from our own, with some good-faith one can see that, in fact, the banana tree is what's being described. The commonness of the banana makes it seem ordinary, but at first encounter and analysis it seems truly bizarre. There is no doubt that we are as bizarre to the unknown, as the unknown is to us. Žižek calls this filter and categorization of the normal  Ideology or the Ideological lens.

    As we see in \textit{Body Ritual Among the Nacirema}, a veiled, yet accurate, description of ourselves can manage to bypass the ideological lens, at which point, and only by this means is this ever truly possible, we can look at ourselves and stand in awe of how bizarre we truly are. Even though Nacirema could be pointed out as not being a true satire, given that by most standards it isn't funny, it's impossible not to see the deeply satirical nature of it, and to draw some parallels with Gulliver's Travels. This same effect can be seen, for example, in the description of the Yahoos, and their addiction to colored stones, a painful description of nothing if ourselves, and in particular of the Bullionist theory that ruled the governing mindset in Swift's time. To bring it back to Lacanian terms, Satire allows us to lift the veil that is the Other (symbolic order) and, through a weakening of the Borromean ring, allow us to see the extraterraneousness of ourselves.

    We live in an age where the value for self-correction has been, by and large, left aside. Social media, with the echo-chambers it provides, has fostered a culture where self-validation through repetition and isolation is the norm. This, perhaps, explains why Satire has changed so much in it's form, we no longer see works like Swift's, or at least they don't rose to fame, because the fundamental dynamic that made it possible is gone. In Gulliver's Travels, we see Swift critique's of the English, and yet his reader is the Englishman himself. This is possible due to the ``veiled critique'' characteristic of his work, by which when the reader realizes he is being critiqued, it is far too late for he has already read and pondered on the work. This has become impossible, partially because the isolation aspect makes critical works, however veiled, difficult to reach their intended audience, but also because work that requires reading and pondering in extension has grown out of fashion. The ``instant delivery'' aspect of modern culture makes it unlikely that any meaningful number of people would go through the trouble of reading something that is longer than a couple of pages, which makes it increasingly harder to construct a through, veiled, and entertaining critique like Swift's work. Interestingly this has caused the satiric dynamic to change dramatically, now each respective side of an issue consumes the satire that was meant for their opponents, since they can and want to see the critique contained in it, as it feeds into their belief-loop. Because of this we have seen the slow disappearing of the veil, transforming satire into mere parody, as is clear from any number of late night shows, who would be categorized as satire, even if they are just comedic-political autofellatio.

    Satire, given its kernel-factor as presented here, requires from the reader some a priori knowledge, namely, it requires some contextual awareness, but must importantly it takes interest in the other. Satire, once more, describes the self of the one being criticized as if it were the (little) other, and therefore it requires the reader to have some interest in the other, since that not being present would making reading the satire pointless at at first (given the delayed realization of the true meaning of the work.) Herein lies the cause for the slow, but steady, disappearance of satire: there is no longer any interest in the other. The central assumption that allows for the satirical delivery, and opens the reader to the material, is by and large gone, and so is true satire.
\end{mla}
\end{document}