\documentclass[12pt]{article}    
    \usepackage[utf8]{inputenc}
    \usepackage{fancyhdr}
    \usepackage{extramarks}
    \usepackage[margin=1in]{geometry}
    \usepackage{amsmath}
    \usepackage{amsthm}
    \usepackage{amsfonts}
    \usepackage{setspace}
    \usepackage{mathptmx}     % Choose Times font 
    \usepackage{microtype}    % Improves line breaks 
    \usepackage{todonotes}
    \usepackage[none]{hyphenat}

    
    
    %
    % Basic Document Settings
    %
    
    \pagestyle{fancy}
    \lhead{\hmwkAuthorName}
    \chead{}
    \rhead{\thepage}
    \lfoot{}
    \cfoot{}
    \rfoot{}
    \renewcommand{\headrulewidth}{1pt}
    \renewcommand{\footrulewidth}{1pt}
    
    \setlength\headheight{15pt} %Slight increase to header size
    
    %
    % Homework Details
    %   - Title
    %   - Due date
    %   - Class
    %   - Section/Time
    %   - Instructor
    %   - Author
    %
    
    \newcommand{\hmwkTitle}{Essay 1 Draft}
    \newcommand{\hmwkDueDate}{September 19, 2017}
    \newcommand{\hmwkClass}{English}
    \newcommand{\hmwkClassTime}{}
    \newcommand{\hmwkClassInstructor}{Professor Joanne Martin}
    \newcommand{\hmwkAuthorName}{Bernardo Meurer}
    
%\newcommand{\note}[1]{\begin{spacing}{1.0}\todo{\small{#1}}\end{spacing}}
\newcommand{\note}[1]{\todo{\setstretch{0.1}\footnotesize{#1}}}
    
    %
    % Title Page
    %
    
    \title{
        \vspace{2in}
        \textmd{\textbf{\hmwkClass:\ \hmwkTitle}}\\
        \normalsize\vspace{0.1in}\small{Due\ on\ \hmwkDueDate\ at 3:55pm}\\
        \vspace{0.1in}\large{\textit{\hmwkClassInstructor\ \hmwkClassTime}}
        \vspace{3in}
    }
    
    \author{\textbf{\hmwkAuthorName}}
    \date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\cleardoublepage
\setcounter{page}{1}
\begin{center}
    \note{Define title}\Large{Placeholder}
    \end{center}
    \doublespacing
    
    Over the course of the past century, college enrollment has had a steady 
    increase, despite the ludicrous raise in cost of attendance. Pricing, in 
    combination with duration, and the uncertainty of graduation, makes it \note
    {Reword?}easy to place doubt on the choice of obtaining a Bachelor's 
    degree. Unintuitively, however, the worth of college has not yet morphed 
    into debt. College, despite the sacrifices it entices, is an investment of 
    unquestionable yields, which are not constrained solely to the financial 
    aspects of life.

    The cost of college has, throughout the last century, \note{Source}risen 
    well above the Consumer Price Index (CPI), yet it's Return on Investment 
    (ROI) remains comfortably positive.

    In the current geopolitical arena, where the main battle is for 
    technological supremacy, skilled workers are more valuable than ever, 
    making the struggle for a degree often times a patriotic one.

    College has immaterial benefits, which is where it's most fundamental value 
    lies, for no other experience will provide you with the growth and 
    improvement that college does.

    Refutations

    Few experiences in life present one with an opportunity to attain both 
    financial and personal growth, and college is perhaps the most 
    quintessential of them. Attending university rewards one economically, 
    mentally, socially, and -- perhaps most importantly -- helps one's country 
    thrive. Cost is but a speck in the vast universe of benefits college 
    provides. Finally, the choice of getting a degree is under more fire than 
    ever before, and yet it is still intrinsically valuable. Graduating is and 
    enlightening and molding experience, that has shaped many of the great 
    women and men of this nation.
\end{document}  