\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
 \usepackage{ifpdf}
\usepackage{mla}
\usepackage{todonotes}


    \begin{document}
    \begin{mla}{Bernardo}{Meurer}{Professor Martin}{English}{September 10, 2017}%
        {More than paper: The value of a Bachelor's degree}
    Over the course of the past century, college enrollment has had a steady 
    increase, despite the ludicrous rise in cost of attendance. Pricing, in 
    combination with duration, and the uncertainty of graduation, makes it easy 
    to place doubt on the choice of obtaining a Bachelor's degree. 
    Unintuitively, however, the worth of college has not yet morphed into debt. 
    College, despite the sacrifices it entices, is an investment of 
    unquestionable yields, which are not constrained solely to the financial 
    aspects of life.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    The cost of college has, throughout the last century, rose well above the 
    Consumer Price Index (CPI), yet it's Return on Investment (ROI) remains 
    comfortably positive. According to the National Center for Education 
    Statistics, the cost of tuition has increased by almost a trifold, even 
    when corrected for inflation. In line with this, however, comes a rise in 
    the average salary of graduates, in his essay ``Is College worth it?'', 
    David Leonhart points out that ``The pay gap between college graduates and 
    everyone else reached a record high last year [2013].'' This is indeed a 
    common theme in discussion on the worth of college, Mary C. Daly \& Leila 
    Bengali argued in their essay ``Is it still worth going to college?'' that
    ``For most Americans the path to higher future earnings involves a 
    four-year college degree,'' and if one looks at the average earnings of 
    those with a bachelor's degree against those without this becomes 
    exceedingly clear. Moreover, Daly \& Leila also show that the average college
    graduate can recover the cost of attendance in under 20 years, which is well 
    in line with the ROI data provided by PayScale, who shows some schools have a
    one million dollar return in just 20 years.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    In the current geopolitical arena, where the main battle is for 
    technological supremacy, skilled workers are more valuable than ever, 
    making the struggle for a degree often times a patriotic one. During the 
    20th century, the world saw an ideological clash of titans: the Cold War. 
    In it, the United States were undeniably the victorious party over the 
    machiavellian Soviet regime. Evidently, what made said victory possible was 
    the technological edge the Americans had over the Soviets; in their essay 
    ``Who Won the Cold War?'', Deudney and Ikenberry confirm this: ``the West 
    held a decisive technological edge''. Presently, a new technological race 
    is pacing, and the contender is now China, a country with vastly more human 
    capital than the United States. The only hope for yet another American 
    victory is for us to specialize efficiently, and outperform them. Jennifer 
    Barret alludes to this in ``What's the value of a college education?'', 
    where she states that ``the country will need 250,000 more engineers over 
    the next 10 years.'' It is trivial to see that, unless each and every 
    American commit strongly to their education, we will not be able to keep 
    up. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    College has immaterial benefits, which is where it's most fundamental value 
    lies, for no other experience will provide you with the growth and 
    improvement that college does. One interesting dimension of this is found 
    in observing the civic behavior of those with a bachelor's degree. We find 
    that they, on average, are more active voters, are more likely to run for 
    office, and are more willing to demonstrate and protest, activities that 
    are fundamental for a working democracy. Moreover, college education leads 
    to a more well informed individual, and one who is likely to make more 
    rational and well-rounded political decisions. Jennie Le in her essay 
    ``What Does it Mean to be a College Grad?'' elucidates well the 
    representativeness of a degree, she states: ``this degree symbolizes my 
    family being able to make and take the opportunities that we've been given 
    in America.'' Le's thoughts echo that of many Americans who see their 
    degree as a validation of the struggle taken by their families to make such 
    an achievement possible. The central point here is that college can be seen 
    not as the means to an end, but as an end in itself. The experience of 
    college (and graduation subsequently) is more than a pathway to employment,
    it molds your personality and morals, and is a deeply transmogrifying 
    process. It is clear and distinct\footnote{Descartian clear and distinct 
    perception} that no person who truly and fully subjects themselves to college will remain unchanged, quite the opposite they will experience growth and introspection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    Independent of the amount of data available, the path of pursuing a college 
    degree will always have an opposition. The economically-minded will argue 
    that it's too high of a cost, ignoring the overwhelming return the 
    investment brings in the long term. Similarly, some will defend that it 
    takes too long to complete, overlooking the fact that a 4-year endeavour 
    represents, according to the CDC, less than 4\% of the median life 
    expectancy. In fact, being a college graduate increases your life 
    expectancy on average. Lastly, to Aristotle's despair, there are those who 
    will cherry-pick data to point out that a degree isn't needed for one to be 
    successful. This statement, albeit true, holds very little meaning since 
    one could argue that, fundamentally, nothing is truly needed for one to 
    achieve success in general. Moreover, the general argumentation behind this 
    is guilty of the Composition fallacy, which turns it from meaningless to nonsensical.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    Few experiences in life present one with an opportunity to attain both 
    financial and personal growth, and college is perhaps the most 
    quintessential of them. Attending university rewards one economically, 
    mentally, socially, and -- perhaps most importantly -- helps one's country 
    thrive. Cost is but a speck in the vast universe of benefits college 
    provides. Finally, the choice of getting a degree is under more fire than 
    ever before, and yet it is still intrinsically valuable. Graduating is and 
    enlightening and molding experience, that has shaped many of the great 
    women and men of this nation.
    
    \begin{workscited}
    \bibent
    Barret, Jennifer. ``What's the value of a college education? It depends'' \textit{CNBC}, 2015. https://www.cnbc.com/2015/06/19/is-a-college-degree-overvalued.html

    \bibent
    Deudney, Daniel, and G. John Ikenberry. ``Who Won the Cold War?'' \textit{Foreign Policy}, no. 87, 1992, pp. 123–-138. JSTOR www.jstor.org/stable/1149164.

    \bibent
    Hansen, Hans. ``Fallacies'', \textit{The Stanford Encyclopedia of Philosophy (Fall 2017 Edition)}, Edward N. Zalta (ed.) https://plato.stanford.edu/archives/fall2017/entries/fallacies.
    
    \bibent
    Le, Jennie. ``What Does it Mean to be a College Grad?'' \textit{Practical Argument: A Text and Anthology}. Ed. Laurie G. Kirszner, Stephen R. Mandell. Boston: Bedford/St. Martin’s, 2014. 41-42.

    \bibent
    National Center for Health Statistics. ``Health, United States, 2016: With Chartbook on Long-term Trends in Health''. Hyattsville, MD. 2017. pp. 116 https://www.cdc.gov/nchs/data/hus/hus16.pdf
    
    \bibent
    National Center for Health Statistics. `` Health, United States, 2016: With Chartbook on Long-term Trends in Health''. Hyattsville, MD. 2017. pp. 57 https://www.cdc.gov/nchs/data/hus/hus11.pdf

    \bibent
    PayScale, ``College ROI Report: Best Value Colleges''. PayScale, 2017, www.payscale.com/college-roi. 

    \bibent
    Snyder, T.D., de Brey, C., and Dillow, S.A. (2016). ``Digest of Education Statistics 2015 (NCES 2016-014)''. \textit{National Center for Education Statistics}, Institute of Education Sciences, U.S. Department of Education. Washington, DC. https://nces.ed.gov/pubs2016/2016014.pdf
    \end{workscited}
    \end{mla}
    \end{document}