\documentclass{article}
    
    \usepackage[utf8]{inputenc}
    \usepackage{fancyhdr}
    \usepackage{extramarks}
    \usepackage{amsmath}
    \usepackage{amsthm}
    \usepackage{amsfonts}
    \usepackage{tikz}
    \usepackage[plain]{algorithm}
    \usepackage{algpseudocode}
    
    \usetikzlibrary{automata,positioning}
    
    %
    % Basic Document Settings
    %
    
    \topmargin=-0.45in
    \evensidemargin=0in
    \oddsidemargin=0in
    \textwidth=6.5in
    \textheight=9.0in
    \headsep=0.25in
    
    \linespread{1.1}
    
    \pagestyle{fancy}
    \lhead{\hmwkAuthorName}
    \chead{\hmwkClass\ (\hmwkClassInstructor): \hmwkTitle}
    \rhead{\firstxmark}
    \lfoot{\lastxmark}
    \cfoot{\thepage}
    
    \renewcommand\headrulewidth{0.4pt}
    \renewcommand\footrulewidth{0.4pt}
    
    \setlength\parindent{0pt}
    
    %
    % Create Problem Sections
    %
    
    \newcommand{\enterProblemHeader}[1]{
        \nobreak\extramarks{}{Problem \arabic{#1} continued on next page\ldots}\nobreak{}
        \nobreak\extramarks{Problem \arabic{#1} (continued)}{Problem \arabic{#1} continued on next page\ldots}\nobreak{}
    }
    
    \newcommand{\exitProblemHeader}[1]{
        \nobreak\extramarks{Problem \arabic{#1} (continued)}{Problem \arabic{#1} continued on next page\ldots}\nobreak{}
        \stepcounter{#1}
        \nobreak\extramarks{Problem \arabic{#1}}{}\nobreak{}
    }
    
    \setcounter{secnumdepth}{0}
    \newcounter{partCounter}
    \newcounter{homeworkProblemCounter}
    \setcounter{homeworkProblemCounter}{1}
    \nobreak\extramarks{Problem \arabic{homeworkProblemCounter}}{}\nobreak{}
    
    %
    % Homework Problem Environment
    %
    % This environment takes an optional argument. When given, it will adjust the
    % problem counter. This is useful for when the problems given for your
    % assignment aren't sequential. See the last 3 problems of this template for an
    % example.
    %
    \newenvironment{homeworkProblem}[1][-1]{
        \ifnum#1>0
            \setcounter{homeworkProblemCounter}{#1}
        \fi
        \section{Problem \arabic{homeworkProblemCounter}}
        \setcounter{partCounter}{1}
        \enterProblemHeader{homeworkProblemCounter}
    }{
        \exitProblemHeader{homeworkProblemCounter}
    }
    
    %
    % Homework Details
    %   - Title
    %   - Due date
    %   - Class
    %   - Section/Time
    %   - Instructor
    %   - Author
    %
    
    \newcommand{\hmwkTitle}{Homework\ \#4}
    \newcommand{\hmwkDueDate}{September 5, 2017}
    \newcommand{\hmwkClass}{English}
    \newcommand{\hmwkClassTime}{}
    \newcommand{\hmwkClassInstructor}{Professor Joanne Martin}
    \newcommand{\hmwkAuthorName}{\textbf{Bernardo Meurer}}
    
    %
    % Title Page
    %
    
    \title{
        \vspace{2in}
        \textmd{\textbf{\hmwkClass:\ \hmwkTitle}}\\
        \normalsize\vspace{0.1in}\small{Due\ on\ \hmwkDueDate\ at 3:55pm}\\
        \vspace{0.1in}\large{\textit{\hmwkClassInstructor\ \hmwkClassTime}}
        \vspace{3in}
    }
    
    \author{\hmwkAuthorName}
    \date{}
    
    \renewcommand{\part}[1]{\textbf{\large Part \Alph{partCounter}}\stepcounter{partCounter}\\}
    
\begin{document}
\maketitle
\pagebreak
\begin{homeworkProblem}
    \textbf{List Stephens' criticisms of college education.}

    \begin{itemize}
        \item ``It [college] rewards conformity rather than independence, 
        competition rather than collaboration, regurgitation rather than 
        learning, and theory rather than application. Our creativity, 
        innovation, and curiosity are schooled out of us.''
        \item ``Failure is punished instead of seen as a learning opportunity.''
        \item ``College fails to empower us with the skills necessary to 
        become productive members of today's global entrepreneurial economy.''
    \end{itemize}
\end{homeworkProblem}
\begin{homeworkProblem}
    \textbf{According to Long, in what sense had ``the conversation [about 
    whether college is a worthwhile investment] become more complicated'' (para. 2)? What ``three important factors'' does she consider?}

    In the sense that College education \emph{may} be worth it; there are 
    factors in play that determine whether or not it's a good choice. The three
    main factors Long lists are:
    \begin{enumerate}
        \item The College a student attends
        \item The field of study
        \item The cost of College
    \end{enumerate}
\end{homeworkProblem}
\begin{homeworkProblem}
    \textbf{What kind of supporting evidence do the writers use? Do you think
    they should have included any other kinds of supports --- for example, 
    expert opinion? Why or why not?}

    The writes mostly rely on \emph{Logos} on their argumentation, relying 
    heavily on data and statistics. I do not believe they should have included 
    other types of support (Pathos, Ethos) because a point that relies solely on
    reason is generally stronger and will withstand heavier scrutiny. In my 
    opinion, Logos is the most fundamental form of argumentation, and a point 
    made solely with it is ideal.
\end{homeworkProblem}


\end{document}