\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage[bottom]{footmisc}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{dialogue}
\usepackage{graphicx,float,wrapfig}
\usepackage[notes,backend=biber]{biblatex-chicago}
\bibliography{journals}

\graphicspath{{./images}}

\title{Journals of Comparative World Religions}
\author{Bernardo Meurer}
\date{\today}

\begin{document}
\begin{spacing}{2}
    \maketitle
    \newpage
    \tableofcontents

    \newpage
    \section{My Religious Views}
        I was born in a farm in the south-eastern part of Brazil, in the state
        of Minas Gerais to be exact. Much like every other family in the state,
        mine was Roman Catholic. I was baptized, as is customary, at a very
        young age, and learned as a kid, from my grandmother, a handful of
        prayers for some different situations. Even though I was raised to be a
        catholic, I no longer identify as one today.

        I think I first started rejecting Catholicism at around the age of 11,
        when my father began insisting that I performed my First Communion.
        Doing so required me to take religion classes twice a week at the local
        church, something I was definitely not interested in. Time went by, I
        never actually performed the first communion, and so I also never
        performed my confirmation at a later age. While one can obviously still
        be a Catholic despite not passing through these processes I feel like
        this first encounter with the bureaucratic apparatus of the Church was
        the beginning of the end for me.

        My first questioning of God came at around the age of 12. I had learned
        from a teacher about Occam's Razor, and so it seemed to me that the
        assumption of God's existence was a fierce violation of that. I could
        not see how presuming the existence of an omnipotent being could be a
        simpler explanation than abstaining from tackling the unfalsifiable
        question of the provenance of existence. It seemed, to me, like a
        comfortable shortcut to some meaningful understanding of the universe as
        it is. At the time I had purchased Schopenhauer's ``The Horrors and
        Absurdities of Religion'', which was a short book of compiled oeuvres.
        From this book one sentence has stuck with me in perpetuity, ``in the
        eyes of the friend of the truth every fraud, however pious, is still a
        fraud''.

        From 12 to about 15 I didn't give the issue of Religion and spirituality
        much thought, it was just not something that was particularly
        interesting to me. When I was 15 my studies into Complexity Theory led
        me to the idea of an Undecidable Problem and to G\"odel's incompleteness
        theorem. I wasn't entirely sure how to concrete relate those to God, but
        I could see that the question of whether or not God existed was a
        decision problem (here in the technical meaning of the term) and that it
        seemed to fall under the undecidable category. I began to notice weak
        parallels between how people usually discussed and spoke of God and the
        recursive proof that G\"odel used to show incompleteness. Later on
        reading Descartes' work this became once again apparent.

        I currently identify as a Spinozist, as in Baruch Spinoza, which
        fundamentally means I believe that our definitions of God and of the
        universe should coincide. I absolutely do not believe in God as a
        conscious entity of any kind, and in many ways Spinozism is nothing but
        a methodical and analytic approach to agnosticism. It is the
        acknowledgment that God is in and of itself existence, and vice-versa.
        In Spinoza's words:

        \begin{description}
            \item[Proposition I] A substance is prior in nature to its affections.
            \item[Proposition II] Two substances having different attributes
                have nothing in common with one another. (In other words, if
                two substances differ in nature, then they have nothing in
                common).
            \item[Proposition III] If things have nothing in common with one
                another, one of them cannot be the cause of the other.
            \item[Proposition IV] Two or more distinct things are distinguished
                from one another, either by a difference in the attributes
                (i.e., the natures or essences) of the substances or by a
                difference in their affections (i.e., their accidental
                properties).
            \item[Proposition V] In nature, there cannot be two or more
                substances of the same nature or attribute.
            \item[Proposition VI] One substance cannot be produced by another
                substance.
            \item[Proposition VII] It pertains to the nature of a substance to
                exist.
            \item[Proposition VIII] Every substance is necessarily infinite.
            \item[Proposition IX] The more reality or being each thing has,
                the more attributes belong to it.
            \item[Proposition X] Each attribute of a substance must be
                conceived through itself.
            \item[Proposition XI] God, or a substance consisting of infinite
                attributes, each of which expresses eternal and infinite
                essence, necessarily exists. (The proof of this proposition
                consists simply in the classic ``ontological proof for God’s
                existence''. Spinoza writes that ``if you deny this, conceive,
                if you can, that God does not exist. Therefore, by axiom VII
                (`If a thing can be conceived as not existing, its essence
                does not involve existence'), his essence does not involve
                existence. But this, by proposition VII, is absurd. Therefore,
                God necessarily exists, Q.E.D.'')
            \item[Proposition XII] No attribute of a substance can be truly
                conceived from which it follows that the substance can be
                divided.
            \item[Proposition XIII] A substance which is absolutely infinite
                is indivisible.
            \item[Proposition XIV] Except God, no substance can be or be
                conceived.
        \end{description}

        The propositions in and of themselves do not constitute a proof of
        Spinoza's ultimate theory (one can read his \textit{Ethics} for that) but
    rather serve to clarify and outlay what I mean by it being an `analytical'
    approach to agnosticism. Finally, and again in Spinoza's words, ``Whatever
    is, is in God, and nothing can be or be conceived without God.''

    \newpage
    \section{Reflections on the Universal Mother}
    Before talking about the Universal Mother specifically, I'd like to talk a
    little about primal religions in general. It is at least mildly curious that
    we tend to call these religious `myths', it sounds like a way to lower their
    value as compared to being a true, institutionalized Religion. Curiously, I
    find that the opposite is true to me, it is exactly their lack of a unified
    apparatus that I find attractive. I deeply believe that the
    institutionalization of Religion is one of the worst things to have happened
    to humanity. Having an institution who operates on a power legitimized by
    themselves and that cannot be forfeited is a horrible idea, as we've seen
    over and over again in the pages of history.

    I am not implying, of course, that primal religions are non-institutional
    due to some conscious decision taken by their respective peoples; I think
    that mostly what kept them from acquiring an operational apparatus was the
    fact that those societies hadn't yet invented bureaucracy.

    Not surprisingly primal religions focus mostly on Nature and it's immediate
    effects on their lives. They are concerned about rain and drought, about
    their crops and livestock, the motions that our environment carries us
    through. I think it is nothing but human to, when faced with great loss
    induced by a natural cause, to attempt to rationalize it. Somehow the
    thought that misfortune might have chosen us randomly and we simply had a
    struck of bad luck is \emph{more} painful than to machine a logical cause
    for it.

    When the crops do fail to yield, then, we seek reason. It must be because
    \emph{I} failed to fulfill some duty, and am now being punished. The success
    of the crop is no longer an unnerving uncertainty bound to the entropy of
    natural behavior, but rather a deterministic side effect of our overall
    actions. Then, if I pray, worship, offer I shall have a good crop. If I
    devote myself to God then He shall reward me with the returns I desire. This
    is more comfortable than to live with the idea that our life hangs on a
    balance with no metric, and that God \emph{does} play dice. This concept,
    however, has always seemed to me somewhat petty or utilitarian; it seems
    like we are almost using God as wishing well to grant us desires. I have
    never been comfortable with the concept that God cares about us in
    particular, or that He would be bothered to inflect on faith based on our
    own actions.

    The Universal Mother is no different from the general outline of primal
    religions contained in the previous paragraph. As the Kagaba said She is
    ``the mother of all our seed, [\ldots] the mother of thunder, the mother of
    streams, [\ldots] the mother of the fruits of the earth, [\ldots] She alone
    is the mother of the fire and the Sun [\ldots] She is the mother of rain.''
    All of this is very much on point with my thoughts on myth as a tool of
    rationalizing Nature's inherent chaos.

    The utilitarian aspect of deity becomes even more apparent on the one
    recorded prayer on text, which says: ``Our mother of growing fields, our
    mother of streams, will [you] have pity on us? \ldots'' It is clear here how
    they position the Mother as the ruler of their fate, the ruler of their
    performance. It's perhaps slightly ironic that the great fear of Humans
    isn't the fact that they control their destiny, for they don't, but rather
    the crushing reality that we do not. And if we do not control the crops and
    their yield, then someone must, and thus She, the Mother, must be managed
    and adored in order to provide for us.

    These fears that I talk about are so deeply entrenched in Human nature that
    here I sit thousands of years later and yet I sometimes find myself wanting
    of someone in control of the odds of my life as well. In the words of
    Antonius Block, from The Seventh Seal, ``We carve an idol out of fear and
    call it God''. What else if not fear and uncertainty motivates us to find
    comfort within God.

    Another quote from Block that I find reflected in the text is his unknowing
    confession to Death himself, ``No man can live faced with Death, knowing
    everything is nothingness''. In the prayer we read ``For [to] whom do we
    belong? Whose seeds are we? To our mother alone do we belong.'' The first
    quote is a powerful scream into the impending void we face as humans; how
    can we deal with our own apparent insignificance and pointlessness? The
    second is a possible answer echoing from the void; we may deal with it by
    accepting our unity with Nature, by removing the virtual layer we've created
    that separates us from the eternal chaos of reality.

    \newpage
    \section{On Hinduism}
    I think the main aspect of Hinduism that I have a gripe with is the
    overwhelming focus on idols and idolatry. I really do not like all of this
    fantasy and anthropomorphism with God, it feels to me almost like a
    marketing strategy to attract the most of followers. It is, in some ways,
    similar to what the Catholic church would do with saints, creating them left
    and right in order to appease everyone they possibly could. God is a
    concept, and a unary one.

    Now, for my dislike of their general mythology I do think there is quite a
    lot of good knowledge in the Vedas, the passages contained within the
    slides, for example, are a small proof of that; ``Do not be led by others,
    awaken your own mind, amass your own experience, and decide for yourself
    your own path''. I think that advice in particular is relevant today where I
    find that most people, in one way or another, live by proxy, wasting away
    while they watch others live through their phones.

    Continuing with the Hindu texts, most of my thoughts on the Upanishads are
    expressed in the next section, but in general I find that the ones I read
    had a boringly mundane, anthropocentric, focus that takes away from the
    truly deep discussions surrounding God.

    It's this same note that I find repeated through Hindu texts and practices
    that somewhat annoy me; it's all far too focused on making God's philosophy
    accessible at all costs. There are stories with fantastical characters,
    there are meanings for all the colors, there are so many Gods one cannot
    keep track, there are multiple reincarnations, and so on. All of this buries
    the \emph{real}, complex, aspects of the concept of God under so much cruft
    and visual aid that it becomes almost pointless. I, for one, do not seek to
    study God to be entertained or engage with a story, I have lots of other
    books for that, I seek God for knowledge, and I'd rather it not be
    suffocated under the weight of so much allegory.

    The last thing I'd like to express about Hinduism is how obviously
    utilitarian and corrupt, and I mean utilitarian in the worst possible sense,
    it is. This becomes obvious the second one looks at the Caste system, which
    might just be the most incredibly evil and effective mechanism of forced
    segregation and social immobilization I have ever encountered. If God wants
    the Caste system, which as a statement in and of itself is flawed for God
    has no desires, then I defy and deny God, for He is nothing but evil.

    The Caste system operates on five different levels (or castes) that form a
    simple, direct hierarchy. On top of the power/holiness distribution are the
    Brahmins (priests), followed by the Kshatriyas (warriors and rulers), the
    Vaisyas (skilled traders, merchants), the Sudras (unskilled workers), and
    finally by the Harijans (outcasts, untouchables). While at first glance it
    might seem that the caste system simply reflects the natural hierarchy of
    society, which is mostly true, it's true evil lies in how caste movement
    works, or rather does not.

    When you are born, you are born in a Caste, usually attached to your family,
    and you stay within that Caste until you die and then perhaps reincarnate
    into a higher Caste. This not only takes away any possibility that through
    real effort one can improve their lives, for they are stuck in their low
    Caste, but does so in a perverse way that forces people to still comply so
    as to no reincarnate into an even lower Caste. It is simply an evil form of
    making sure the masses comply with the oppression of their rulers, and I
    think the most obvious indicator that the whole system is a sham is that
    \emph{of course} the priests are on top of the hierarchy.

    I could go on about what's wrong with the Caste system for days on end, but
    I think I have made my general thoughts on it rather clear: disgust. I have
    not much else to say about Hinduism, other that I have no interest in
    something that creates and endorses such a system.

    \newpage
    \section{Thoughts on \emph{Katha Upanishads}}
    The thing I find most interesting about the Katha Upanishads texts is the
    similarities in plot to Ingmar Bergman's \emph{The Seventh Seal}. In the
    text we are told the story of Nachiketas, a yogi who receives the blessing
    of three wishes from Death. Death grants his first two wishes without
    reprieve, but the third goes differently. ``When a man dies, this doubt
    arises: some say `he is' and some say `he is not'. Teach me the truth.''
    Asks Nachiketas. ``Even the gods had this doubt in times of old; for
    mysterious is the law of life and death. Ask for another boon. Release me
    from this''. Replied Death.

    This reminds me deeply of one of the last exchanges between Block and Death.
    \begin{dialogue}
        \speak{Death} When next we meet, the hour will strike for you and your friends.
        \speak{Block} And you will reveal your secrets?
		\speak{Death} I have no secrets.
		\speak{Block} So you know nothing?
		\speak{Death} I am unknowing.
    \end{dialogue}

	Ever since I first heard this dialogue it has struck me as one of the
	scariest and most unnerving thoughts possible. The idea that Death Himself
	does not know truly what awaits those whom he reaps is a deep stare into
	the void that is the Unknown, for if Death is unknowing, then who can claim
    otherwise? The thought that our ultimate destiny is unknown to all is truly
    terrifying.

    Katha Upanishads, however, takes a different turn than Bergman's movie; in
    the text Death does know what happens after the reaping. On the omnipresent
    theme of seeking mechanism of control over the seemingly random reality, in
    the story Death provides Nachiketas with the knowledge of immortality.

    If taken at face value, which is as I understand the Hindus take the story,
    I don't really find it interesting or productive. These attempts to take
    control of that which lies beyond us by definition always seem to me as a
    cheap way to avoid the true issue, which is our inherent unknowing.

    Another interpretation of the text, and one that I am personally more fond
    of, it to take it as an allegory. Here we take immortality not literally,
    but rather to mean that if one acts correctly and lives a wise, humble, good
    life than they will become immortal; not in and of themselves but through
    the memory and love from the world around them.

    In the text, the path is described as ``Only when Manas (mind) with
    thoughts and the five senses stand still, and when Buddhi (intellect,
    power to reason) does not waver, that they call the highest path. That is
    what one calls Yoga, the stillness of the senses, concentration of the mind,
    It is not thoughtless heedless sluggishness, Yoga is creation and
    dissolution''. In my reading this is the preaching of a life in abstention
    of the mundane and of deeply focused introspection.

    One section of the text I truly dislike is when Death says to Nachiketas
    ``This sacred knowledge is not attained by reasoning; but it can be given by
    a true Teacher''. For me the moment some knowledge cannot be attained by
    reasoning then it is not knowledge, but fraud and, to cite Schopenhauer
    again, a fraud, however pious, is still a fraud.

    Note that what I mean by `fraud' in the previous paragraph I don't
    mean to say that the statement is \emph{false}, that would also be a fraud,
    all I mean is that the statement is either unfalsifiable, or that the text
    does not truly provide backing or reason for it. This is part of why I so
    heavily dislike the ``This sacred knowledge is not attained by reasoning''
    passage; knowledge can only be attained by reason, and to say that some
    knowledge escapes that rule is to escape the burden of proof that should lie
    on all those who make true statements.

    \newpage
    \section{Reflections on Jainism and Sikhism}
    I am a deep believer in `productive' faith. What I mean by this is that I
    think faith should lead the disciple to not just internal betterment and
    happiness, but also to improving the world around him and focusing on making
    their lifetime impacting. I think that based on this parameter it should
    come as no surprise that I was not very keen on the ideals of Jainism.

    First of all I agree with the principle of no aggression; to a degree. I
    \emph{do} think that a hypothetical world without violence but just
    diplomacy would be better, but as I think is accepted, such world is not
    ours. I think, then, that Jainism in it's search for non-violence goes
    simply too far. For one to have to brush while one walks, and to wear a mask
    so as not to disturb the insects is simply counter productive. There is so
    much more good one could be doing with their time and effort than wasting
    away on these minimalisms.

    Now, the five ethical principles of Jainism are:
    \begin{enumerate}
        \item Nonviolence
        \item Truthfulness
        \item Non-stealing
        \item Chastity
        \item Non-possession, non-attachment from people, places, things
    \end{enumerate}

    While 1--3 seem to be very reasonable ethical principles, and overall
    good basis for a good society, thew remainder are quite the opposite. 4 is
    if nothing else a recipe for human extinction, if we are to expect all to be
    ethical, and 5 is the key ingredient in a society which doesn't advance, and
    doesn't improve. The curious thing is that element 5 is in many ways
    directly opposed to 1, since technology and it's comforts spare us so much
    pain and violence. These might be feasible or desirable principles for a
    monk, although I would question that as well, but they are most definitely
    not desirable values for society as a whole.

    For all the flaws that I see in Jainism, I see perfection in Sikhism. They,
    for one, affirm that God is beyond human comprehension, which is to me one
    of the few reasonable assumptions to be made about God. Secondly, they
    present a heavy focus on the individual path towards spirituality, ``there
    is One Truth, each must find their own path to it''. The idea that many
    other religious doctrines have that there is one true path to God and all
    must follow it equally is, to me, counter productive and leads to a general
    feeling of inadequacy (something which I felt deeply from Catholicism).

    Sikhs solve one of the main issues with Religion, and in particular with
    institutionalized religion, which is the idolatry, in the more literal sense
    of God. The conversion of God as a concept and goal into God as an idol of
    worship, usually also attached to the anthropomorphization of God, is the
    spark that lights religious wars. Idolatry makes the mind weak, it shifts
    the focus away from the things that truly matter withing the concept of God.

    In the same line, I find that the three guiding principles of Sikhism are
    almost as good as one could hope for, as opposed to the nonsensical five of
    Jainism. Namely, they are:
    \begin{enumerate}
        \item \emph{Naam Japna} --- Remember God at all times; be aware of
            yourself as if you were watching someone.
        \item \emph{Kirat Kana} --- Honest wealth; participate in life. To
            engage in life, work and earn a livelihood honestly is how we grow
            (rejection of asceticism).
        \item \emph{Vand Chakna} --- Sharing wealth, becoming a guardian of
            one's community.
    \end{enumerate}
    These principles yield the absolute opposite of what I criticized the
    Jainist ones for, they are good seeds for a working, productive, healthy
    society and life. The first principle reminds us to be mindful, and to never
    let the goal of spirituality off our minds. The second principle encourages
    an honorable life, a life of work, development and growth. The third
    principle reminds us that we are not islands, that we are always part of a
    community and that we should do out very best to improve it and perfect it,
    to help those within it without pride or reprieves.

    Finally, I think my overall liking of Sikhism can be well summed in this
    phrase: ``The primary subject of the Guru Granth Sahib is Truth, and how to
    become a person of truth. It enables men and women to lead meaningful lives
    while being members of a society''. This is exactly what I believe Religion
    should focus on, not petty idolatry but how we can find our meaning in life.

    \newpage
    \section{Meditations on Buddhism}
    I'd like to start my thoughts on Buddhism by focusing on the Eightfold Path,
    and primarily on what I believe to be it's fundamental flaw; the fact that
    it's entirely prescriptive and not \emph{descriptive}. What I mean by this
    is that while the Eightfold Path tells us \emph{what} to do, it does not
    illuminate us on \emph{how} to do it, which arguably is the most important
    piece of information.

    \textbf{Right View:} The first step states that one must have an
    understanding of the `problem'. The issue here is, I think, clear; often
    times it is precisely understanding the problem that is the most challenging
    step. I, for one, have wasted away effort attempting to solve a problem I
    did not have, or that I misunderstood, and here the Eightfold Path gives us
    no aid.

    \textbf{Right Intent:} This might be the one path that could be seen as
    \emph{both} descriptive and prescriptive, but sadly this is only true
    because it is so vacuous. It simply states one's need to focus on the
    process, which is a fair prescription to almost anything.

    \textbf{Right Speech:} Yet again the path tells us to be aware of what our
    speech reveals of our character, but provides no clues on how exactly should
    one be able to evaluate that. Without some form of metric or guidance this
    becomes nigh impossible; we can never truly see ourselves through the eyes
    of the other. As Lacan would perhaps put it, our perception of ourselves is
    itself an Alter Ego, bundled together with the other Alter Egos that
    encompass our perceptions of others.

    \textbf{Right Conduct:} Here, the Buddha gives what could generally be seen
    as good advice; to become aware of one's own motives and to move towards
    simplicity, but this is mostly tainted by, again, the lack of description.
    The real challenge here is how do we become aware of our motives, truly, and
    a solution to it is nowhere to be found in the Path. Moreover the
    ruling of chastity before marriage and of teetotalism are simply counter
    productive to a truthful, working society.

    \textbf{Right Livelihood:} This is the one path where the Buddha is truly
    descriptive; don't slave, don't prostitute yourself, and don't sell poison
    (drugs). If expanded, however, it is difficult to argue that most jobs don't
    oppress other beings in one way or another.

    \textbf{Right Effort:} Here the Buddha focuses on \emph{how} one must strive
    for enlightenment. Unfortunately, however, he is oblivious regarding how can
    one know when they are ``seeing things are they are''.

    \textbf{Right Mindfulness:} My biggest gripe here is with the idea that the
    mind is powerful enough that it can master all things. This is simply not
    true, in Mathematics we are often faced with concepts which the mind cannot
    master, which is why we have notation to aid us. The mind cannot master the
    general motion of 11-dimensional linear transformations on a convex
    manifold, for example.

    \textbf{Right Concentration:} This Path is actually very much descriptive,
    and for the most part it details the process of meditation. The one thing
    that is opaque here is the idea of how can one know they have mastered
    meditation and concentration; the parameters are simply too loosely defined
    and difficult to verify.

    Now, while I may question the usefulness of the Eightfold Path, I cannot
    disagree the Marks of existence. All three of its statements, that all
    formations are impermanent, subject to suffering, and without a self, are
    very precise, and I think a good guide on the nature of our own existence.
    \newpage
    \section{On Confucianism}
    On this section, I would like to discuss my personal take on
    \emph{Chun-Tzu}, what I think of each of its elements, and of it as a
    whole. The \emph{Chun-Tzu} is Confucius' term for a person with a fully
    evolved character, or a noble person. To be a noble person, then, is to:
    \begin{itemize}
        \item Not grieve that others do not recognize one's merit. One's only
            anxiety is failing to recognize theirs.
        \item Not preach what one practices until one practices what they
            preach.
        \item Take as much trouble to discover what is right as lesser people
            take to discover what will pay.
        \item Covet the reputation of being slow in word, but prompt in deed.
        \item Not accept people because of what they say, nor reject saying
            because the speaker is what he is.
        \item Never go on eating till one is sated, to not demand comfort in
            one's home, to be diligent in business and cautious in speech, to
            associate with those that possess the Way, and to correct one's own
            faults.
        \item Be ashamed to let one's word outrun their deeds.
        \item Have a mind that can see questions from all sides, without bias.
        \item Be calm and at ease.
        \item Be able to influence those who are above them.
        \item Be distressed at one's own lack of capacity, and never at others'
            failure to recognize one's merits.
        \item Make demands upon oneself, not others.
        \item Call attention to the good in others, and not to their defects.
        \item Balance substance and ornament
        \item Never be unhappy.
        \item Never be perplexed.
        \item Never be afraid.
    \end{itemize}

    These are not precisely what the texts say, but a slightly boiled down
    version that I think remains true to the source. To me, then, to be fully
    human is to be fully and wholly moral, according to the above parameters.
    One of the things I find most interesting about Confucianism here is that I
    do not disagree with the parameters put for for \emph{Chun-Tzu}. Usually I
    find religious morals and ``inner goals'' to be full of inconsistencies,
    impossibilities, or undue vagueness; but here this is not the case at all.

    Throughout my reading I have found that, for the most part, Confucius'
    concepts of a full human are almost directly aligned with my own. I think of
    a full human as someone who is in control of their own lives, and who
    chooses to live rightfully, even when that might prove difficult.

    I find that, beyond the text in question, there is tremendous wisdom to
    Confucius' work. He overall presents a very careful and well constructed
    code, which I think remains supremely relevant to this day.

    \section{Thoughts on Taoism}
    In Taoism, I would like to explore the concept of \emph{Wei Wu Wei}, the
    action of non-action or ``creative quietude.'' I find this to be one of the
    most intractable concepts we were exposed to in class, and even after
    reading on it multiple times, I still do not feel like I completely capture
    its meaning.

    Now, my thoughts on the ``actionless activity'' are quite a bit fluid.
    Sometimes I feel like I've grasped it's true meaning, only to see that
    illusion fade briefly after; like trying to clench water. The texts describe
    \emph{Wei Wu Wei} as:
    \begin{enumerate}
        \item Act without doing anything, and teach without saying anything,
            things arise, when things arise let them come, when things disappear
            let them go. Have, but don't possess, act but don't expect. When
            your work is done, forget it. That is why it lasts forever.
        \item Practice not-doing, and everything will fall into place.
        \item Fill your bowl to the brim, and it will spill. Keep sharpening
            your knife, and it will blunt. Chase after money and security, and
            your heart will never unclench. Care about people's approval, and
            you will become their prisoner. Do your work, then step back. The
            only path to serenity.
    \end{enumerate}
    I think the above sections portray \emph{Wei Wu Wei} as a mentality of
    ``going with the flow.'' In many ways, I deeply believe that I already apply
    this to my daily life. In particular I find the advice to `Have, but don't
    possess' to be particularly powerful.

    I think \emph{Wei Wu Wei}, obtuse as it is conceptually, feels extremely
    natural. Somehow it is as if reading about it brings me no closer to
    understanding it, and yet I understand it somehow. It is as if the creative
    quietude is within me, and I am able to identify it whence reading, but
    somehow the words on the paper simply do not capture it, do not do it
    justice.

    In particular, having left my country at an early age, there is one comment
    that I like particularly
    \begin{itemize}
        \item A good traveler has no fixed plans, and is not intent upon
            arriving \ldots
    \end{itemize}
    This truly could not be more true, the beauty of traveling is never in
    arriving, as Saramago put it ``You always arrive somewhere.''

    \newpage
    \section{Reflections on Judaism}
    Reading from the Torah's description of the creation of the world, a few
    things caught my attention. Firstly, there I wonder whether the fact that
    ``God saw that the light was good, and God separated the light from the
    darkness'' implies somehow that God had action on that choice. By which I
    mean, is light inherently good, and God merely perceives that, or did God by
    action create light and darkness and embedded into them their wills. I find
    that this is a tough thread to sow, mostly because it becomes very easy to
    arrive at a conundrum where either God created darkness, which seems
    unideal, or that God had no control over darkness' existence, which would
    put his omniscience in check. It's a curious interaction, already in the
    first day of creation.

    Another thing that I find curious, and if the Torah were to have been found
    by some future race that had no idea of it's existence, it's how
    unapologetically anthropocentric it is. They dedicate a paragraph to the
    first day, then skim over the next five days where \emph{literally
    everything else was created}, and jump over to the sixth day for the
    creation of Humankind. I found it almost funny that crucial things like the
    sky, the earth, vegetation, the Sun, the Moon, and all the other animals are
    completely brushed over.

    The sixth day chapter is the one I find most problematic. Fundamentally, it
    portrays earth and all it's beauty and worth as being in service of Man,
    Nature is ours to take so we can ``fill the earth and master it.'' If this
    mentality isn't what has driven us full throttle into the climatic chasm we
    now find ourselves in, I do not know what did. Our belief that the inhuman
    is inherently lesser and here to become utilitarian to us is very misguided
    and dangerous.

    On the seventh day God declares a holiday because he was done setting up His
    universe. Being the cynic what I am I find it hard to believe that even had
    this not been the case at all, whomever was writing the holy texts would
    find a way to squeeze a holiday in. Curiously though, I find that today more
    than ever the Jewish Sabbath is of crucial importance. Having a day dedicate
    to reflection, away from work and technology is an absolute blessing in
    today's world. I don't really understand the fasting, however.

    Moving on to the Primacy of Deeds there are some interesting, albeit
    somewhat obvious to me, texts. The initial paragraph creates a parallel
    between knowledge and branches, and deeds and roots. The idea is that deeds
    are fundamentally more important than knowledge, for they ground us. I'm
    not sure whether I agree with this, but I'm incline to find it almost
    disrespectful. It's also not clear to me why acquiring the knowledge isn't
    itself a deed, or what exactly is supposed to be a deed here.

    Following the roots story, comes a parable and here I must really say my
    ability to comprehend text falls short, because it feels to me like this
    passage could be one of my grandfather's ramblings. I really don't
    understand what's so hard about buying wine without a vessel, and I also
    don't understand why the Torah must only be taught to those who can offer
    good deeds. If anything the paragraph left me more confused than anything
    about the whole `deeds' discussion that is going on.

    We continue with some lessons from Rabbi Hillel, the first one being him
    metaphorically blasting a heathen into outer space. Jokes apart, he does
    manage to sum up the Torah's \emph{Gestalt} very well and briefly, although
    I'm not sure how much I believe in him when he says ``the rest is
    commentary.''

    Lastly Rabbi Hillel seems to have read some of Kierkegaard's work on
    despair, because much like the first page of \emph{The Sickness Unto Death},
    I have absolutely no idea what ``If Not Now, When?'' Is about. It certainly
    feels like there is a point being made here, it's just hidden under so much
    semantic plumage that I find it hard to extract anything from it.

    \newpage
    \section{Impressions of Christianity}
    We begin our study of Christianity with the Beatitudes, an absolute classic
    and very famous text. I find the Beatitudes to be, if nothing else, a cry
    for those oppressed and marginalized in the society. This becomes clear once
    you see the people Jesus addresses: ``blessed are those who hunger and
    thirst \ldots blessed are the peacemakers \ldots blessed are those who have
    suffered persecution for the cause of right \ldots blessed are those who
    show mercy \ldots''

    To me the Beatitudes are a very short code of ethics from God. It outlines
    the virtues and the virtuous acts that will yield God's good faith.
    Unfortunately though, some parts of the Beatitudes are either too vague or
    too loose for it to be regarded as an actual code of ethics. The parts
    regarding the sorrowful, for example, isn't a very good fit. Moreover,
    saying that those whose hearts are pure shall see God opens the question of
    what exactly does it mean to have a pure heart. The Beatitudes, then, fail
    to be a compelling ethical guideline.

    Regarding the relationship between the Beatitudes and structures of power, I
    think the main conflicts are rather obvious. For starters they speak nothing
    of rulers or divine right, usually those would be added to appease the
    nobility. Moreover, the Beatitudes directly speak of those who hunger and
    suffer persecution, which are clear, direct, stabs at the local government
    and their ethno-politics. Lastly, it seems like the Beatitudes completely
    omit the existence of worldly power as of any importance to God, which is a
    huge invalidation of the general rationale for a government's establishment.

    Moving on, I'd like to talk about a section of The Gospel of Thomas,
    \emph{The Kingdom} in particular. In it, we read ``\ldots the father's
    kingdom is spread out upon earth, and people do not see it.'' I think this
    is an absolutely invaluable insight into Jesus' view of Heaven. Firstly,
    Heaven does not exist as some external entity of perfection, but rather it
    exists within earth, and within us. We live in heaven, we just do not see
    it, and in our not seeing we allow ourselves to defile and destroy it.
    Heaven might be a Godly concept, but it is in our realm, it is amidst us, we
    need not seek its location, but rather we need seek its conceptual
    representation, and where and how Heaven exists among us.

    To me, then, Heaven (loosely) represents perfection at a higher level, and
    what I mean by that will become clearer in a moment. Perfection in my eyes
    can only be found by seeking that which is rare and extraordinary, a perfect
    world is one filled with rarities and miracles; and yet is this not exactly
    the world we live in? Think about every single interaction between two
    things; people, animals, objects, molecules, etc. Think about how many
    distinct outcomes could have been produced by each atomic step of those
    many-fold interactions. It is clear that at any given moment an infinitude
    of these interactions are happening, and from the realm of all
    possibilities only one materializes itself. How truly amazing it is, then,
    that we live in the world we do; how different could it have become if one
    were to change perhaps a single one of those interactions.

    Our reality is the composition of a near infinitude of minimal interactions
    between objects, and as Quantum Mechanics teaches us, many of those
    interactions appear to happen completely and entirely at random. Is it not,
    then, heaven that we live on? Do we not live on a land of miracle and
    rarity?

    We must realize that the kingdom is this universe which we live on, and the
    earth we inhabit. We must cherish and protect it, for there is no other,
    this is the Kingdom of God, and it has come to us since the beginning of
    existence.

    \newpage
    \section{Meditations on Islam}
    We begin this short meditation by analyzing some of the paragraphs of
    \emph{True Islam is Kindness} from the \emph{Hadith}.
    \begin{description}
        \item[a.] \textbf{Golden Rule} --- No one is a true believer unless he
            desireth for his brother that which he desireth for himself.
        \item[Commentary] Apart from some of the inherent flaws that come from
            this sort of philosophy, better exposed through Kant's work, the
            Golden Rule is generally good.
        \item[b.] \textbf{Fellow-Beings} --- Do you love your Creator? Love your
            fellow-beings first.
        \item[Commentary] What I find interesting here is that they very clearly
            use `Fellow-Beings' and not `brother' to identify that this extends
            to non-Muslims as well.
        \item[c.] \textbf{The Mark of Faith} --- Kindness is a mark of faith:
            and whoever hath not kindness hath not faith.
        \item[Commentary] This brings me back to the Beatitudes a little. As
            much as I want to like this item I find that `kindness' is such a
            vague word that it is easy to subvert it. What if I consider
            kindness to kill heathens because I will be sparing them of their
            own misery?
        \item[d.] \textbf{Good to God's Creatures} --- All God's creatures are
            His family; and he is the most beloved of God who doeth most good to
            God's creatures
        \item[Commentary] I find it curious reading this passage that more
            Muslims aren't vegetarian or vegan. It would that the Hadith extends
            `do no harm' to animals as well.
        \item[e.] \textbf{Actions Most Excellent} --- What actions are most
            excellent? To gladden the heart of a human being, to feed the
            hungry, to help the afflicted, to lighten the sorrow of the
            sorrowful, and to remove the wrongs of the injured.
        \item[Commentary] This seems to just hit on the same note regarding
            kindness again; and again I find the comment I made on c relevant;
            what if I consider me killing a heathen as me helping his terminal
            affliction?
        \item[f.] \textbf{The Needy} --- Feed the hungry and visit the sick,
            free the captive, if he be unjustly confined. Assist any person
            oppressed, whether Muslim or non-Muslim.
        \item[Commentary] The main thing that I find interesting here is the
            freedom given to free those unjustly captured, that is quite a lot
            of power, and this sort of mentality would later be the cause of
            some of the main criticisms to John Locke's work. Moreover, I find
            that the extension of this to non-Muslims is very interesting.
        \item[g.] \textbf{The Perfect Muslim} --- That person is not a perfect
            Muslim who eateth his fill, and leaveth his neighbors hungry.
        \item[Commentary] What I find more particular here is that it somewhat
            reminds me of Sikhism, and in particular with regards to the focus
            on forming a solid community where one can depend on the other.
        \item[h.] \textbf{The Aged} --- Verily to honor an old person is showing
            respect to God.
        \item[Commentary] I don't disagree with this, but I do feel like it
            lacks some context. \emph{Why} is it showing respect to God?
        \item[i.] \textbf{Goodness} --- Follow up an evil deed by a good one
            which will wipe [the former] out, and behave good-naturally to
            people.
        \item[Commentary] Besides not knowing what `good-naturally' means, this
            has me thinking about what sort of economy of sin exists within
            Islam. How does one know which good act is good enough to wipe out a
            given sin?
        \item[j.] \textbf{Ultimate Jihad} --- The most excellent Jihad is that
            for the conquest of the self.
        \item[Commentary] I really like this point, and I think it provides
            great clarification as to what does Jihad truly mean.
    \end{description}

    I think it's easy upon reading these messages, to quickly jump to
    conclusions that (mostly) Shia Muslims who commit heinous crimes are simply
    not following their own morals. To some degree this might be true, but it is
    also important to remember that the Shia muslims recognize less Hadiths than
    the Sunni muslims, and so some of this philosophy is simply invalidated for
    them.

    Of anything that I've read about Islam, the above passage is most definitely
    the best in terms of setting a moral tone for the religion, unfortunately it
    is found in the Hadith and not in the Quran. It is not immune, however, to
    the usual vagueness that I find plagues most religious texts and leaves far
    too much room for interpretation.

\end{spacing}
\end{document}
